---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ESAT (Ecological Site Analytical Tools)

<!-- badges: start -->
<!-- badges: end -->

The goal of ESAT is to provide tools for analysis of the tabular and spatial configuration of Ecological Site Concepts in SSURGO (Soil Survey Geographic Database) products. 
..

## Installation

You can install the development version of ESAT like so:

``` r
remotes::install_github("brownag/ESAT")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ESAT)

# get "all" condition aggregation via Soil Data Access for selected soil survey area(s)
x <- es_aggregate_ssurgo("CA041")

# decompose dominant condition site codes 
es_decompose_site_code(x$site1)

# check aggregate condition percentage
x$agg_pct_r <- es_calculate_aggregate_sitepct(x)
table(x$agg_pct_r)

# inspect one mapunit with aggregate site percentage <100%
x[which(x$agg_pct_r == 80), ]
```

## Spatial Check Example

_TODO_
